---
title: "Analysis"
author: "*Compiled on `r date()` by `r Sys.info()['user']`*"
output: 
  html_document:
    toc: true
    toc_float: yes
    number_sections: true
    theme: cerulean
    highlight: haddock
    includes: 
  pdf_document:
    toc: true
editor_options: 
  chunk_output_type: console
---

## Summary
Mixed Logit Analysis on the DRCE conducted in Indonesia and Mexico. Split into four different models; Standard opt-out model (Model I), Pooled (Model II), Unforced Responses (Model III), and Forced Responses (Model IV).

## Data Source 
Personal Interviews
 
## Reference 
Panga Watch
 
## Downloaded
September 30, 2019
 
Time range: 
2019
 
## Format
comma separated values

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(survival) # for clogit
library(stargazer)
library(coefplot)

# might use these
library(xtable)
library(here)
library(kableExtra)

master_survey <- read.csv("master_survey_resp.csv", stringsAsFactors = TRUE) %>%
  select(-start, -end, -survey_type, -interviewer, -comment, -text_vms_adoption, -fishery_problem_one, -fishery_problem_two, -fishery_problem_three, -fishery_solution_one, -fishery_solution_two, -fishery_solution_three, -photo)

```

## Standard opt-out model (Model I)
```{r}

standard_opt_out <- read_csv("int/standard_opt_out_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt)

standard_clogit <- clogit(RES~ASC+sos+info+own.fisher+own.industry+own.gov + strata(survey_version), data=standard_opt_out) # run the clogit. ASC represents the alternative specific constant, or the opt out option.
summary(standard_clogit)

```


## Pooled (Model II)
```{r}

pooled <- read_csv("int/pooled_data_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt) %>%
  mutate(own = as.factor(own))

pooled <- within(pooled, own <- relevel(own, ref = 1))

# pooled_clogit<-clogit(RES~sos+info+ own + strata(STR), data=pooled)
# summary(pooled_clogit)

pooled_clogit<-clogit(RES~sos+info+  own.fisher + own.industry  + own.gov + strata(STR), data=pooled)
summary(pooled_clogit)

# This is used as "model 1" in our paper to showcase conditional logit results 

```


```{r}

# make the graphs for actual preference weights

sos_coef <- pooled_clogit$coefficients[1]
info_coef <- pooled_clogit$coefficients[2]
own_1_coef <- pooled_clogit$coefficients[3]
own_2_coef <- pooled_clogit$coefficients[4]
own_3_coef <- pooled_clogit$coefficients[5]

pooled_clogit_coefs <- data.frame(names = names(pooled_clogit$coefficients), clogit_coef = pooled_clogit$coefficients)

avg_own <- (own_1_coef + own_2_coef + own_3_coef)/4
avg_info <- (info_coef)/2
avg_sos <- sos_coef/2

sos_actual <- pooled_clogit_coefs %>%
  filter(names == "sos") %>%
  mutate(actual = clogit_coef - avg_sos)

sos0_actual <- data.frame(names = "sos0", 0, actual = -sum(sos_actual$actual)) %>%
  rename("clogit_coef" = "X0")

sos_actual_final <- rbind(sos_actual, sos0_actual)

sos_actual_final <- rbind(sos_actual, sos0_actual)

info_actual <- pooled_clogit_coefs %>%
  filter(names == "info") %>%
  mutate(actual = clogit_coef - avg_info)

info0_actual <- data.frame(names = "info0", 0, actual = -sum(info_actual$actual)) %>%
  rename("clogit_coef" = "X0")

info_actual_final <- rbind(info_actual, info0_actual)

own_actual <- pooled_clogit_coefs %>%
  filter(str_detect(names, 'own') ) %>%
  mutate(actual = clogit_coef - avg_own)

own4_actual <- data.frame(names = "own.public",  0, actual =-sum(own_actual$actual)) %>%
  rename("clogit_coef" = "X0")

own_actual_final <- rbind(own_actual, own4_actual)

all_actual <- rbind(sos_actual_final, info_actual_final, own_actual_final) %>% 
  select(-clogit_coef)
# write.csv(all_actual, "output/pooled_clogit_actual_coefs.csv", row.names = FALSE)

# all_actual <- read_csv("output/pooled_clogit_actual_coefs.csv")

# previous two lines commented out b/c I do not have a output folder to write it to, this is a remnant from Gage's work

positions <- c("sos", "sos0", "info", "info0", "own.fisher", "own.industry", "own.gov", "own.public")

all_actual %>%
  ggplot(aes(x= names, y= actual)) +
  geom_col() + 
  theme_bw() +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(breaks = seq(-1.3, 1.3, 0.1)) %>%
  labs(y = "Preference Weights")

```

##Unforced Responses (Model III)
```{r}

unforced <- read_csv("int/unforced_data_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt)

unforced_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+strata(STR), data=unforced)
unforced_clogit
```

##Forced Responses (Model IV)
```{r}

forced <- read_csv("int/forced_data_fix.csv") %>%
  left_join(master_survey, by = "survey_id") %>%
  select(-noalt)

forced_clogit<-clogit(RES~sos+info+own.fisher+own.industry+own.gov+own.public+strata(STR), data=forced)
forced_clogit
```


**Likelihood Ratio Test Taken from Penn et al.**
```{r}
#K = 5
#M = 2

pooled_log <- logLik(pooled_clogit) #-74.11078 (df=5)
unforced_log <- logLik(unforced_clogit) #-42.90397 (df=5)
forced_log <- logLik(forced_clogit) #-22.24721 (df=5)

-2*(logLik(pooled_clogit) - (logLik(unforced_clogit) + logLik(forced_clogit)))
-2*(pooled_log- (unforced_log + forced_log))

-2*(74.11078 - (42.90397 + 22.24721)) #17.9192
# if this then 17.9192 < 20.52 which means that we do not reject the null that there is no difference between the forced and unforced........... need to write this up formally

```

Methods Log Lik Test:
We can test the effect of forced choice versus unforced choice using a likelihood ratio test for equality. The test statistic is:

$$ -2*(LL_{r} - \sum LL{u}) $$
Which is chi-squared distributed with K(M-1) degrees of freedom, where K is the number of restrictions (5), M is the number of treatments (2). The null hypothesis of the test is that the parameters are not significantly different between treatments. This means that if we do not reject the null, we can use the standard opt out method without worry of respondent bias. If the test statistic exceeds the critical value, found in the chi square table, then evidence suggests that the treatments sufficiently contribute to explaining the model and reject the null hypothesis of no difference between the forced and unforced datasets. 


## Stargazer table and coefficient plot of pooled model
```{r, results = 'asis'}

# Table
final_table <- stargazer(pooled_clogit, type = "html")

# Plot
final_plot <- coefplot(pooled_clogit, color = "black") +
  scale_y_discrete(name="Feature",labels=c("SOS Feature","Non-Private Information","Fisher Owned Data","Industry Owned Data","Government Owned Data")) +
  theme_classic()
final_plot

```


## Make pooled predictions using predict()
reasoning for predicting out a clogit model:

https://markmail.org/search/?q=list%3Aorg.r-project.r-help+predict+clogit#query:list%3Aorg.r-project.r-help%20predict%20clogit%20from%3A%22Therneau%2C%20Terry%20M.%2C%20Ph.D.%22+page:1+mid:tsbl3cbnxywkafv6+state:results

https://stackoverflow.com/questions/35329585/how-to-get-fitted-values-from-clogit-model

```{r}
#predictions for pooled data

library(AlgDesign)
ffd <- gen.factorial(c(2,2,4), varNames = c("sos", "info", "own"), factors = "all") # construct a full factorial design which has two 2 level attributes and one 4 level attribute. factors = "all" indicates that all arguments are factors
ffd 

all_packages <- ffd %>%
  mutate(STR = 1001) %>% 
  mutate(sos = ifelse(sos==2,1,0), info=ifelse(info==2,0,1)) %>%
  mutate(own.fisher=ifelse(own==1,1,0), own.industry=ifelse(own==2,1,0), own.gov=ifelse(own==3,1,0), own.public=ifelse(own==4,1,0)) 

#pooled_predictions <- predict(pooled_clogit, newdata = pooled, type = "expected", se.fit = TRUE) #this gives relative probs within strata. 

pooled_predictions <- predict(pooled_clogit, newdata = all_packages, type = "risk", se.fit = TRUE) #this gives absolute probabilities.


pooled_predictions_data <- data.frame(all_packages, pooled_predictions) #%>%
  #select(STR, package, info, sos, own, RES, fit)

# sos	0 = no, 1 = yes
# info 	1 = non, 0 = anon
# own	1 = fishers, 2 = industry, 3 = govt, 4 = public access
#adopt : 1 = accept, 0 = decline

pooled_predictions_data_final <- pooled_predictions_data %>%
  mutate(level_probs1 = fit/(fit+ 1),
         level_se = se.fit/(se.fit + 1)) %>%
  select(-fit, -se.fit, -STR) %>%
  arrange(-level_probs1) %>%
  select(info, own, sos, own.fisher, own.industry, own.gov, own.public, level_probs1, level_se) %>%
  mutate(info = case_when(
    info == 0 ~ "Anon",
    info == 1 ~ "Non-Anon"
  ),
  own = case_when(
   own == 1 ~ "Fishers",
   own == 2 ~ "Industry",
   own == 3 ~ "Government",
   own == 4 ~ "Public Access"
  ),
  sos = case_when(
    sos == 0 ~ "No",
    sos == 1 ~ "Yes"
  )) %>%
  rename("Probability" = "level_probs1",
         "SE" = "level_se")

pooled_predictions_data_final

```

```{r}

# Table of pooled model predition results

table_predictions <- pooled_predictions_data_final %>% 
  mutate(probability_pct = Probability*100) %>% # add new column that transforms probability to percentage
  select(info, own, sos, probability_pct, SE) %>% # rearrange column order and drop other columns
  mutate_if((is.numeric), round, 2) # round all numeric columns to 2 digits


probability_table <- kable(table_predictions, col.names = c("Information","Ownership","Safety","Probability (%)", "SE")) %>% 
  kable_styling(full_width = F, position = "center")
probability_table


```

